PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-17 qfenv_paper/qf_environment.tex
More edits on QF Section

%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. With far more mass galaxies in high env than in low env.

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section describe the stellar mass distribution of our galaxy population and reveal the evolution of this distribution over comic time. We compare the quiescent and the star-forming populations, using the SMFs, in order to quantify the fraction of galaxies that have depleted their star-formation - the quiescent fraction. Adding environment classifications to our analysis, we investigate the effects of environment on the quiescent fraction and its evolution. By comparing the quiescent fraction evolution between high and low environments we are able to isolate and quantify the effects of environment dependent external quenching mechanisms as opposed to the internal mechanisms that operate within the galaxy.

From the SMF number densities ($\Phi$) the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins.

@@

%Remark on the difference between low environment and high environment.

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}
%fiducial mass may be 11.0 depending on what we want.

>>>>

%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. 
%Remark on the clear mass-density relation: more massive galaxies in high environment 
% Compare to Bolzonella et al. 2010 and perhaps even Bundy et al. 2006 results
% Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.

\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations using the quiescent fraction - the fraction of galaxies that have depleted their star-formation. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments. By analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the redshift evolution of the quiescent fraction for a complete mass range in our environments. Through this comparison we reveal the subtle effects of environment in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed quenching mechanisms that operate on the scale of our environment measure, such as strangulation and ram-pressure stripping (CITECITE).

From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the darker shading represent lower redshift bins.

@@

% color-mass relation, mass-density relation, color-density relation, SFR-density relation, SSFR-density relation,

% SDSS QF matches with SDSS QF of Tinker et al. 2010 who uses a group catalog. The PRIMUS QF values match reasonably well with zCOSMOS 10k in Iovino et al. 2010 and zCOSMOS 20k in Kovac et al. 2014, once disparities between color classification and SFR classifications are taken into account.

% The mass dependence of each subsample QF: reflects the color-mass relation and the morphology-mass relation
% The "color-mass" relation holds for both low and high environment galaxies. While others in literature (Cucciati et al. 2010) found that the mass dependence was less apparent in high environment, this does not hold true for the SDSS and PRIMUS data. Although this could be due to the contamination in our environment measurements since there are large redshift errors. 
% Emphasize that due to the limited mass range from mass completeness limits, the conclusions on mass dependence should be taken with a grain of salt. 
% The redshift evolution of the QF in each 
\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_fidmass10_5_lit_primuszerr.eps,height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}
%fiducial mass may be 11.0 depending on what we want.
